### 2014-03-03 seminar/seminar_report/chapter1.tex
change

\section{Motivating Scenario}\label{sec:motexample}

In this section, we present a scenario and demonstrate why there
is need for communities of services. We first propose an example
of a real world scenario, focusing on user experience. There are a
plethora of options available to people in today's society,
including weather forecasting, ticketing services, map services,
local places guides and so on. Most mobile or web applications
cannot independently satisfy users requests and should rely on
different online services. The high competition within the
services industry requires applications to use reliable and high
quality online service providers.

If the user were to check a web site or run an application on her
mobile device upon having downtime, or having high response delay
or encountering any non-satisfying quality metric, she will
instantly remove the application, which is a huge business concern
for application providers. For example, if a user installs a
ticketing application on her mobile device and the application is
not using high quality service providers, the user would instantly
uninstall the application, which has an extremely negative impact
on the
visibility of the application. %Let us say you search "Montreal
%Weather" on a search engine and you click on a web site which is
%slow because it is using a bad weather web service as source of
%its raw data, the user will leave the web site and try another
%link from search results, which has a bad Search Engine
%Optimization (SEO) effect for the web site, and search engines
%would not show that web site on search results anymore, which is a
%business and revenue loss for the application.
Thus, end user satisfaction is the main goal for competitive
online providers. Communities of web service, by providing
services with higher quality, higher uptime and reliability for
end users, aim to reach this goal. To this end, community
management decisions should capitalize on important QoS parameters
while forming the community and during membership management.

High demand on online services has created a massive business
competition. For example, nowadays users are provided with
multiple choices of web services offering local places information
such as coffees, venues, and shops nearby a geographic position.
It is hard for new web services to find their customers and be
visible for end users amongst hundreds or thousands of other
available services, even if they provide a high quality of
service. Hence, the concept of communities of web services
provides them with the chance of joining a platform with an
established market share and reputation. However, it is crucial
for a community manager to consider many factors when inviting or
accepting new members. For example, if the market share is not big
enough, bringing new web services can cause revenue drop for the
already residing members. This may encourage other web services to
collude, leave, or join other communities, hurting the community
stability. This is an important issue which has not been addressed
previously in the relevant literature. On the other hand, if
communities bound the number of web services to ensure higher
revenue, availability and response time could be negatively
affected if some members encounter problems. This is because
alternative web services for substitution will be limited.  This
has also not been efficiently addressed in the related work.
Consequently, community formation algorithms satisfying some
desirable properties such as community stability and overall
revenue are yet to be defined considering end users, community
managers and service providers.

@@

Web service communities are dynamic by design
\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
services are modeled as intelligent autonomous agents, where they
can adopt a strategy maximizing their payoff at any time. A web
service can ask joining a community and has the right to leave it.
Community managers can invite or ask a web service to leave in
order to maximize the community profit. Users can simply stop
sending requests to a web service which is not providing
satisfactory services. Thus its important to consider all the
parties involved in the decision making process about the
community management. Most of the recent work on communities of
services are either user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.
Our initial research question is: \emph{How can we model the
community of agent-based services in order to maximize the utility
of involved users, web services and community organizers?}

In order to address this problem, recently
\cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In
\cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. The issue with these solution concepts is that they
consider community as a whole and model it as one entity in their
formulations. A community master decides on behalf of all the
members using an aggregated function of parameters. This can hurt
the overall revenue for some individual web services, or even a
subset of web services. Those services can collude and form their
own community and gain more, instead of having to adjust and share
their resources with other members. Another important issue which
needs to be considered is the community stability. In community of
web services, the members and community organizers collaborate to
perform tasks. Having jointly completed a task and generated
revenue, they need to agree on some reasonable method of dividing
profits (or tasks) among themselves. This is a key issue for the
group stability still to be investigated. If the revenue sharing
mechanism is not fair enough for any subset of web services
working in the community, these agents, as profit maximizing
entities, would just deviate and make their own group. So an
important research question that we would like to address is:
\emph{How can we model fair and stable communities as coalitions
of agent-based web services?}

%The consideration of those inputs is a significant
%issue as existing web services can lose utility or payoff because
%of the new member, which can results in an unhealthy and unstable
%group. The problem comes from the fact that the existing members
%should collaborate with the new web services, so probably their
%performance as a group can suffer. Existing members may even
%deviate and try to join other communities if they are unsatisfied.
%Those considerations of forming stable and efficient coalitions
%are the main contributions of our paper.

%However, a high
%performing web service could deviate anytime it finds itself
%unsatisfied within the community instead of adjusting its service
%parameters.

@@

% ooooooold
%\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
%\begin{itemize}
%\item How much are agents certain about selecting a move at each dialogue step?
%\item How much are agents certain about their dialogues?
%\item How good are agents in the real dialogue (i.e. the effective dialogue)?
%\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
%\end{itemize}
%Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.

@@

\section{Proposal Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in
Chapter~\ref{sec:MAS} the background needed for our research along
with relevant related work. Chapter~\ref{sec:coalitionformationws}
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter~\ref{sec:conclusionfuturework}, we present our conclusion,
future plan, and the timetable of our research.

>>>>

@@

Web service communities are dynamic by design
\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
services are modeled as intelligent autonomous agents, where they
can adopt a strategy maximizing their payoff at any time. A web
service can ask joining a community and has the right to leave it.
Community managers can invite or ask a web service to leave in
order to maximize the community profit. Users can simply stop
sending requests to a web service which is not providing
satisfactory services. Thus its important to consider all the
parties involved in the decision making process about the
community management. Most of the recent work on communities of
services are either user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.

Recently
\cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In
\cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. The issue with these solution concepts is that they
consider community as a whole and model it as one entity in their
formulations. A community master decides on behalf of all the
members using an aggregated function of parameters. This can hurt
the overall revenue for some individual web services, or even a
subset of web services. Those services can collude and form their
own community and gain more, instead of having to adjust and share
their resources with other members. Another important issue which
needs to be considered is the community stability. In community of
web services, the members and community organizers collaborate to
perform tasks. Having jointly completed a task and generated
revenue, they need to agree on some reasonable method of dividing
profits (or tasks) among themselves. This is a key issue for the
group stability still to be investigated. If the revenue sharing
mechanism is not fair enough for any subset of web services
working in the community, these agents, as profit maximizing
entities, would just deviate and make their own group.

@@

@@

\section{Report Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in
Chapter~\ref{sec:MAS} the background needed for our research along
with relevant related work. Chapter~\ref{sec:coalitionformationws}
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter~\ref{sec:conclusionfuturework}, we present our conclusion,
future plan, and the timetable of our research.

### 2014-03-03 seminar/seminar_report/chapter3.tex
change

@@

>>>>

\section{Competitive behaviour of services within communities}\label{s:coop}

In previous sections, our focus was on community formation and we the focus was on cooperative behaviour of the web services as agents. However competition within cooperative environments, for business agents having different set of capabilities. Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}. In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite. However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure. Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section. we propose a mechanism within which service agents
in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this paper interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task. We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate). In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility. We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.

\subsection{The Proposed Framework}\label{The Proposed Framework}
In this section, we first present the architecture of the proposed
model. We explore the characteristics of intelligent service
agents and their network. We link this architecture to the
implemented system where we investigate the services' coopetitive
attitudes. We compute the involved system parameters and explain
the services' interactive strategy profiles by highlighting their
coopetitive choices.

\begin{figure}[h]
\centering
\includegraphics[scale=1]{architecture++.eps}
\caption{Services are partitioned into competitive and cooperative
sets. Competitive services may get tasks directly from the master
agent and they can share it with other cooperative services in
their collaborative networks within the same community.}
\label{architectureFigure}
\end{figure}

\subsubsection{The Architecture}

Figure \ref{architectureFigure} illustrates the architecture of a
typical community aggregating a number of services with different
interactive strategies. Some of them compete for the task where
they directly deal with the master. Some others cooperate in the
associated task where they only deal with the competed service as
the task leader and do not directly interact with the master (the
master deals only with the service that has bid for the task,
which is responsible of choosing its collaborative network). In
both sets, some service agents are for certain moments out of any
collaboration network. We highlight details of the interactive
strategies in the rest of this section.
%Figure \ref{algorithm1} %exposes the details of task allocation mechanism that is used to select the web services.
In the proposed system, the master sorts the competing services
(i.e., the bidders) based on some parameters (such as reputation)
that we explain in the rest of this section. The winner to which
the master allocates the task is the bidder
service agent that is ranked first. %If the web
%service is busy or unwilling to take the task, the master
%allocates the task to the second competing web service in the
%list.
There is a chance that some tasks could not be assigned to any
service. These tasks are accumulated in the task pool to be
allocated in the next task allocation round. Upon allocation of
the task, the service is responsible for offering the required QoS
that is stated in the task being generated by a consumer.
Afterwards,  the master rewards or penalizes the competing
service by upgrading or degrading its reputation according to the
offered QoS compared with the required one. This comparison
influences the sorting mechanism used by the master to allocate
the tasks in further task allocation rounds.

%ok til here

\subsubsection{System Parameters}
In this section, we demonstrate the involved parameters and their
corresponding formulations and explanations.

\textbf{Task QoS} ($T_{QoS}^r$) is the required QoS metric for a
specific task $r$. Users define tasks with specific QoS
requirements such as response time, availability, and
successability (or accuracy). We aggregate and
normalize these metrics to a value between $0$
and $1$. %Throughout this paper, we refer to this value as
%$T_{QoS}$.

\textbf{Service QoS} ($QoS_w^r$) is the QoS provided by the
service $w$ after performing the task $r$. Again, the metrics that
contribute in computing this QoS are aggregated and normalized to
a value between $0$ and $1$. The offered quality might or might
not meet the required task quality $T_{QoS}^r$. In the latter
case, the service user would be disappointed and a negative
satisfaction feedback is expected. In our proposed system, both
cases are considered when calculating the services' reputation.

%\textbf{NTD} is the number of tasks completed by a web service.

\textbf{Budget} ($B_w^t$) is the amount of money the service agent
$w$ has in its disposal during the window time $t$ (i.e.,
$[0,t]$), which helps pay for the community membership fees
($\epsilon$) and is one of the parameters that the service agent
considers when deciding about getting involved in a competition or
not.

\textbf{Reputation} ($Rep_w^t$) is a significant factor in any
online community \cite{Fouss:2010:PRM:1751668.1751727}. Without a reputation enabling
mechanism, users cannot differentiate among services, specially
the ones which offer the same type of service. Reputation
mechanisms usually aggregate users' experiences and in our case it
strongly depends on QoS that each service provides. Users define
tasks, each one with specific quality $T_{QoS}^r$, so that after
performing a certain number of tasks, each one with $QoS_w^r$,
during a window time $t$, the reputation of $w$ gets evaluated by
the master agent. $Rep_{w}^{t}$ refers to the reputation of $w$
during that window time $t$.

In Equation \ref{repr}, we compute the reward that the master
computes considering the task $r$'s QoS $T_{QoS}^r$ compared with
the service offered quality $QoS_w^r$. In case the offered quality
meets user expectations, the reward value would be positive. In
this system, we consider a small value as default rewards $\eta$
which the master considers together with the proportional level of
satisfaction as a weighted value (by $\upsilon$). In this case,
the higher the offered quality, the more weighted reward. In case
the offered quality did not meet the user expectations, the reward
would be negative. A default penalty value $\rho$ (where
$\rho>\eta$) together with the weighted proportional difference
are therefore considered. The idea is to harshly penalize the
services rather than rewarding them. To this end, rational service
agents should carefully analyze their capabilities once the
available tasks are announced. Equation \ref{reward} computes the
obtained reward by $w$ during the window time $t$ considering the
set $task_w^t$ of tasks performed by $w$ during the window time
$t$. In our proposal, service agents have the goal of increasing
their budget, which is directly related to their reputation. Thus,
they have to decide strategically how to maximize this value.

\begin{equation} \label{repr}
reward_w^r = \begin{cases}
\eta + \upsilon \frac{QoS_w^r}{T_{QoS}^r+QoS_w^r}   & \text{if $T_{QoS}^r\leq QoS_w^r$;}\\
-(\rho +  \upsilon \frac{T_{QoS}^r}{T_{QoS}^r+QoS_w^r} ) & \text{otherwise.}\\
\end{cases}
\end{equation}

\begin{equation} \label{reward}
reward_w^t =
\begin{cases}
\frac{\sum_{r \in
task_w^t}reward_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}

The assigned reputation value is updated by the computed reward
value. The computed reputation of services is bounded by the
minimum and maximum reputation values $0$ and $1$. % to constrain
%the balance the cooperative community of web services. The updated
Let $\Gamma = Rep_{w}^{t} + reward_w^t$. The updated reputation
value is then computed as follows:

\begin{equation}\label{repz}
%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
%\end{equation}
%\begin{equation*}
Rep_{w}^{t+1} = \begin{cases}

\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
0  & \text{if $\Gamma < 0$;}\\
1 & \text{if $\Gamma > 1$.}\\
\end{cases}
\end{equation}
%
For new services with no previous reputation value, we use the
bootstrapping trust technique proposed in \cite{conf/icwe/YahyaouiZ11}. This
technique consists in giving the new services a chance and observe
their behaviors for a period of testing time. The observation
sequence is modeled as a hidden Markov model that is used to
detect the behavior of the service by comparing the observation
behavior against pre-defined trust patterns. Based on the matching
result, an initial value is assigned to the service. Using this
initial reputation value, services quickly converge to their
actual and stable values using the update function.

\begin{proposition}\label{Complexity-Rep}
$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
linear in the size of the window $t$.
\end{proposition}

\begin{proof}\footnote{In this paper, we
assume that the common arithmetic and elementary functions, such
as multiplication, division and trigonometric functions can be
computed in time $O(1)$ as they operate on inputs of fixed sizes.}
The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
works by storing the last calculated reputation value in a
variable, so it will not be recalculated again at each iteration.
However, the calculation of $reward_w^t$ is needed. Since the
function $reward_w^t$ can be computed in time linear in the number
of tasks (see Equations \ref{repr} and \ref{reward}), which in
turn is linear in the size of the window time, the result follows.
$\Box$
\end{proof}

\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
services' performance based on their recent strategies and
activities. Growth factor is relative to services' reputation
$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
$B_w^t$. This factor is the main variable a typical service uses
to decide about which strategy to adopt. The details about the
decision making process are described in Section \ref{Theoretical
Results}. We use Equation \ref{eq:growthfactor} to compute the
growth factor $G^t_w$ of the service $w$ during the window time
$t$ as the average of the three aforementioned parameters, where
$n_t$ is the total number of offered tasks to the whole community
during the
window time $t$, %(we consider the time window $t$ large enough so
%that $n_t \neq 0$),
$\mu_w$ is the mean received service fee, and $\epsilon$ is the
cost of community membership.

\begin{equation}\label{eq:growthfactor}
G^t_w = \frac{Rep^t_w + QoS_w^t+\frac{B_w^t}{n_t  \mu_w -
\epsilon}}{3}
\end{equation}
\begin{equation*}
\mu_{w} \in\{\mu_{w, CM}, \mu_{w, CO}\},~~~QoS_w^t =
\begin{cases} \frac{\sum_{r \in
task_w^t}QoS_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation*}

This equation is designed so that it satisfies the following
desirable properties:

\begin{enumerate}

\item The growth factor function should be monotonically
increasing in the offered quality of service $QoS_w^t$.

\item The growth factor function should be monotonically
increasing in the service's reputation $Rep^t_w$.

\item The growth factor function should be monotonically
increasing in the budget $B_w^t$ if the maximum possible profit is
positive and monotonically decreasing in $B_w^t$ if the maximum
possible profit is negative. This property reflects the idea that
the budget contributes in the increase of the growth factor as far
as there is a chance to make profit. In fact, the contribution of
the budget $B_w^t$ in the calculation of the growth factor should
be proportional to the maximum possible profit $n_t \mu_w -
\epsilon$ where the service $w$ receives all the offered tasks
during the window time $t$.

\end{enumerate}

  % if the profit $\beta_w$ made by the web service $w$
%considering the mean received service fee $\mu_w$ and the cost of
%community membership $\epsilon$ is positive.
It is easy to show that Equation \ref{eq:growthfactor} satisfies
the three aforementioned properties by calculating the partial
derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
first partial derivatives is positive and the sign of
$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
maximum profit $n_t \mu_w - \epsilon$, so we are done. The mean
service fee depends on the strategy adopted by the service because
a competitive service receives higher fees $\mu_{w, CM}$ compared
to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
The motivation behind this is that a competitive service for a
given task is the leader for that task while other cooperative
services are performing specific subtasks as asked by the leader.

\begin{proposition}\label{Complexity-Growth_Factor}
$G_w^t$ can be computed in time linear in the size of the window
$t$.
\end{proposition}

\begin{proof}
As shown in the second part of Equation \ref{eq:growthfactor}, the
function $QoS_w^t$ can be computed in time linear in the number of
tasks, which in turn is linear in the size of the window time.
Since $B_w^t$ is constant, the result follows from Proposition
\ref{Complexity-Rep}. $\Box$
\end{proof}

\subsubsection{Service Interactive Strategies}

The main goal of each individual service agent is to increase its
income (payoff). This income can be earned from tasks (or
requests) done by this service. In our model, services can decide
to compete to get a task from the master agent or to cooperate
with other services within a given collaborative network (the way
a collaborative network is set by a leader is based on the
cooperative services reputation and their QoS parameters that
should coincide with the required QoS). Therefore we define two
types of service strategies. First, when a service has higher
level of confidence based on its growth factor, it can compete to
get a task from the master and adopts the competitive strategy.
Second, when the service agent has a lower level of confidence
that it does not feel capable to compete, it waits for some other
services to cooperate with to perform some tasks \footnote{Through
the paper, requests or tasks are supposed to be decomposable.},
and thus it adopts the cooperative strategy. Services estimate the
outcome of all the strategies and choose one of them accordingly.
This decision is not static but can change over time so service
agents can switch from one strategy to the other, and this dynamic
attitude is referred to as coopetition.

@@

\subsection*{Coopetitive behaviour of services within communities}\label{sb:resutlscoop}

In this section, the objective is to investigate the effectiveness of the proposed strategic system in section \ref{s:coop}.

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this paper (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive). The proposed model's
reasoning mechanism enables services to effectively select their
interacting strategies and the obtained budget represents the best
outcome over the strategic decision making procedure they run all
the time. This procedure avoids cases where a service selects the
competitive strategy but gets refused to obtain a task from the
master. The procedure allows services to make decisions that
maximize their utilities, so that if the service cannot compete,
the procedure would suggest to collaborate, which is better than
competing and failing to obtain the task. In this case (i.e.,
competing and not getting the task), the service stays idle but
still pays the community membership fee, which means losing
utility. The developed strategic decision making mechanism leads
some service agents to follow cooperative strategies that overall
maintain an optimal community budget. In the same figure, we
observe the cumulative budget of a community where services follow
random interacting strategies. The outcome is clearly lower
because services at each run randomly decide over their acting
strategies. This potentially influences the community budget
because a low quality service if randomly selects to follow the
competitive strategy, it will fail to perform a task with high QoS
requirements. This kind of strategy selection is totally
stochastic while the task allocation algorithm follows a logical
path. The ideal system is the one that analyzes the optimal
strategic path and consistently follows strategies that bring
maximum outcome. The result regarding the community that follows
the random strategy shows how stochastic decision making degrades
the community budget, but still this result outperforms the one of
the purely competitive community. In this purely competitive case,
all the services follow the competitive strategy and the frequency
of getting rejected from a task is relatively high. In a community
with limited number of tasks, the competitive strategy for all
services highly influences the community budget because a
potential group of services are losing at every run.

The results illustrated in Figure \ref{Graph1} part (a)  verify
the importance of the strategic decision making procedure to
logically decide over the possible competitive and cooperative
choices. Figure \ref{Graph1} part (b) illustrates communities
average reputation of involved services. The graphs represent the
influence of the rewards that the master agent uses to encourage
highly capable services to compete for a task. As for the
cumulative budget, we observe that the coopetitive community
outperforms the random coopetitive and competitive communities in
terms of average reputation. The proposed model's average
reputation increases because services follow optimal strategies
where they can perform better so obtain higher rewards. For the
same reasons as for the cumulative budget, the average reputation
of the random coopetitive community
outperforms the one of the competitive community. %The idea is to balance web
%services' strategies to maintain optimal community budget.

\begin{figure}%[h]
%\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[scale=0.47]{graphbgtmed.eps}
\includegraphics[scale=0.47]{graphrep.eps}
\caption{Part (a): Cumulative community budget comparison. Part
(b): Average community reputation comparison over different
strategic decisions.} \label{Graph1}
\end{figure}

 %Figure \ref{Graph2} part (a) illustrates the reputation of the proposed $Coopetitive$ community where
 %we highlight the range of reputation change in the community. The vertical lines denote the range of %reputation that is associated with the master web service. The rewards and penalties applied to %different
% web services show that the master web service over runs extends the reputation range and takes %control of the whole community. In the developed model, web services are encouraged to choose
 %optimal strategies. This is maintained over growth factor comparison of the $Coopetitive$ web %services.

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{graphbgtmed3set.eps}
\includegraphics[scale=0.35]{graphbgthigh.eps}
\includegraphics[scale=0.35]{graphbgtveryhigh.eps}
\caption{High membership fees or less task income impacts on
different selection strategies. Part (a) Medium membership fee.
Part (b) High membership fee. Part (c) Very high membership fee.}
\label{membership_fee_graph}
\end{figure}

In Figure \ref{membership_fee_graph}, we analyze the scenario
where the membership fee is high, which is analogous to situations
where the task income is low. We need to verify how well services
can perform in these situations. Figure \ref{membership_fee_graph}
part (a) depicts the results in a normal scenario. In part (b), we
have increased the membership fee to the high amount of 5 units
per run. Services will need to pay $5$ units on each iteration of
tasks being offered. As results, the strategic coopetitive
decision making process helps services make benefits, but
stochastic and compete methods lead to lose income since making
mistakes and trying to compete for jobs the services cannot afford
while having to pay higher membership fees is making them lose
budget in a faster pace. In part (c), the membership fee is higher
than an average income that
a task can generate. %It might not be rational for selfish
%self-interest web services to stay in these communities from the
%utility perspective, but as mentioned there might be other
%political reasons they might need to stay in these communities. As
The simulation shows that the stochastic and compete strategies
make services budget decreases drastically. However, our strategic
coopetitive decision making process loses budget in a slower pace.

In Figure \ref{Graph2} parts (a) and (b), we observe the
competitive and cooperative probability of four different services
where two of them ($w_1$ and $w_3$) are following optimal
strategies as suggested by our model (competitive for $w_1$ and
cooperative for $w_3$) and the two others ($w_2$ and $w_4$) are
following non-optimal strategies, which are the opposite of what
our model suggests. Over elapsing runs, services that follow
optimal strategies bring best reputation. In fact, the master
agent rewards the high quality service that chooses the
competitive strategy, cooperates with other peers and successfully
accomplishes the task. In this system, the reputation regarding
such a service is increasing over time and the possibility of
allocating further tasks is increasing as well. By increasing the
growth factor, such a service (here shown as $w_1$) increases the
probability of selecting the competitive strategy. On the other
hand, the other service (here shown as $w_2$) that is incapable of
competing is penalized by the master agent because the offered
quality might not meet the required task quality. Thus, $w_2$
degrades its growth factor by following the competitive strategy.
As intelligent entity, this service is encouraged to change its
strategy to the cooperative one and thus, its probability of
selecting the competitive strategy is decreasing over time. We
have similar results in Figure \ref{Graph2} part (b) regarding
services $w_3$ and $w_4$ where unlike $w_4$, $w_3$ is
strategically following the cooperative strategy allowing for an
increase in the
overall reputation. %Therefore, $w_4$ is more seeking the
%competitive strategy where it can increase its growth factor.

\begin{figure}[h]
%\centering
\includegraphics[scale=0.47]{graphcomp.eps}
\includegraphics[scale=0.47]{graphcoop.eps}
\caption{Reputation progress of four different services: W$_1$ and
W$_3$ are following our strategic decision model; W$_2$ and W$_4$
are following the opposite.} \label{Graph2}
\end{figure}

In our model, services are managed by selfish agents in the sense
they try to maximize their own utilities. We analyze how their
strategies affect the social welfare, and from user's and
community's point of view how good the tasks are being performed.
This directly impacts user's satisfaction and community's
reputation in general. The Higher quality and quantity of tasks
performed leads to higher user's satisfaction for the community
which results in better reputation for the community. The results
in Figure \ref{graph_task} show the quality and quantity of tasks
being done successfully in three communities adopting the three
different aforementioned strategy decision algorithms. Part (a)
depicts the number of tasks successfully done. When services are
not capable of performing tasks alone and decide to compete for
tasks with high QoS requirements, they usually fail to perform the
task. However, if they opt for cooperating although they have less
income, they have higher chance of performing tasks
collaboratively with other services. Figure \ref{graph_task}, Part
(b) shows the probability of successfully performing tasks, which
influences users' satisfaction. The results show that services
using our coopetitive strategy when deciding whether to compete or
cooperate have higher chance to get high satisfaction ratio
compared to stochastic and compete strategies. The quality of
tasks performed are depicted in Figure \ref{graph_task} Part (c).
The figure shows the average QoS of tasks successfully
performed. %Collaborating increases the performed QoS of tasks,
%therefore forming collaborative groups improves user satisfaction.
As clearly confirmed by the simulation, the coopetitive community
outperforms the stochastic and compete communities.

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{graphtaskdone.eps}
\includegraphics[scale=0.35]{graphtasksatisfaction.eps}
\includegraphics[scale=0.35]{graphavgqostask.eps}
\caption{Overall performance from community's point of view. Part
(a) Total number of tasks successfully done. Part (b) Ratio of
tasks satisfied with required QoS. Part (c) Average QoS of
performed tasks.} \label{graph_task}
\end{figure}
